\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-08-12 manuscript/main.tex
new file:   analysis/.Rhistory 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

\author[1]{Guoying Deng}
\author[2]{Xuyuan Zhang \thanks{Email Address: \href{mailto:zxuyuan@umich.edu}{zxuyuan@umich.edu}}}
\affil[1]{School of Economics, Sichuan University, China}
\affil[2]{Department of Economics, University of Michigan, United States}

>>>>

\author[1]{Guoying Deng} % dengguoying@scu.edu.cn
\author[2,3]{Li Gan} % ganli@tamu.edu 
\author[4]{Xuyuan Zhang \thanks{Email Address: \href{mailto:zxuyuan@umich.edu}{zxuyuan@umich.edu}}}
\affil[1]{School of Economics, Sichuan University, Chengdu, China}
\affil[2]{Department of Economics, Texas A\&M University, College Station, TX, USA}
\affil[3]{Survey and Research Center for China Household Finance, Southwestern University of Finance and Economics, Chengdu, China}
\affil[4]{Department of Economics, University of Michigan, Ann Arbor, MI, USA}
